Examining the impact Overturn of Roe v. Wade: Banning of Abortion on Infant Mortality Rates in the United States Using a Difference-in-Differences Approach

### 2024-11-24 paper/paper.qmd
update paper

The structure of this paper is organized as follows: @sec-data provides
details on the data sources and variables used in our analysis.
@sec-model explains the modeling approach, including the assumptions and
specifications of our linear regression framework. In @sec-result, we
present our findings, emphasizing the key predictors of Harris's
support. Finally, @sec-discussion explores the implications of our
results and suggests potential directions for future research.
[Appendix- @sec-data-details] provides external data detail, [Appendix-
@sec-model-details] provides model detail, @sec-c provides an datasheet,
and @sec-d provides an detailed introduction of surveys, sampling and
observational data in our paper.

@@

@@

# Results

@@

# Discussion

>>>>

The structure of this paper is organized as follows: @sec-data provides
details on the data sources and variables used in our analysis.
@sec-model explains the modeling approach, including the assumptions and
specifications of our linear regression framework. In @sec-results, we
present our findings, emphasizing the key predictors of Harris's
support. Finally, @sec-discussion explores the implications of our
results and suggests potential directions for future research.
[Appendix- @sec-data-details] provides external data detail, [Appendix-
@sec-model-details] provides model detail, and [Appendix-@sec-survey] provides an detailed introduction of surveys, sampling and
observational data in our paper.

@@

# Model {#sec-model}

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
